Temporal trends (NAMCS)

### 2017-08-01 ms1/namcs_trends.Rmd
update analysis

dx_visit = dx %>%
  filter(!is.na(diagnosis_type)) %>%
  mutate(dummy=TRUE) %>%
  select(visit_id, diagnosis_type, dummy) %>%
  distinct() %>%
  spread(diagnosis_type, dummy) %>%
  mutate_if(is.logical, function(x) if_else(is.na(x), FALSE, x))

@@

abx_visit = top_abx %>%
  select(desc, abx) %>%
  left_join(drugs, by='desc') %>%
  count(visit_id, abx) %>% ungroup() %>%
  #mutate(present=n>0) %>% select(-n) %>%
  #spread(abx, present) %>%
  #mutate_if(is.logical, function(x) if_else(is.na(x), FALSE, x))
  spread(abx, n) %>%
  mutate_at(vars(-visit_id), function(x) if_else(is.na(x), 0L, x))

visits = read_tsv_years('../../db/namcs/data/namcs_visits_%i.tsv') %>%
  mutate(age_group=case_when(.$age <= 19 ~ 'child',
                             .$age <= 64 ~ 'adult',
                             .$age <= 92 ~ 'elderly')) %>%
  left_join(dx_visit, by='visit_id') %>%
  left_join(n_abx, by='visit_id') %>% replace_na(list(n_abx=0)) %>%
  left_join(abx_visit, by='visit_id') #%>%
  #mutate_at(top_abx$abx, function(x) if_else(is.na(x), 0L, x))
```

@@

```{r per_capita_models_display}
x = per_capita %>%
  filter(term=='year') %>%
  mutate(valid=abs(std.error/estimate)<=0.3, adj.p.value=p.adjust(p.value, method='BH')) %>%
  add_pct_change()

read_tsv('tables/model_abx.tsv') %>%
  filter(term=='year', model=='poisson') %>%
  left_join(top_abx, by=c('antibiotic'='medicare_abx')) %>%
  mutate(abx=if_else(is.na(abx), antibiotic, abx)) %>%
  mutate(data_source='medicare') %>%
  bind_rows(per_capita %>% filter(term=='year') %>% mutate(data_source='namcs')) %>%
  add_pct_change() %>%
  mutate(abx=forcats::fct_reorder(abx, pct_change)) %>%
  ggplot(aes(x=abx, y=pct_change, ymin=ci_low, ymax=ci_high, color=data_source)) +
  #geom_linerange() +
  geom_errorbar() +
  geom_point() +
  coord_flip() +
  xlab('') +
  ylab('pct change in consumption per capita') +
  ggtitle('Per capita') +
  theme_minimal()

x %>%
  select(abx, ci_low, pct_change, ci_high, p.value, valid, adj.p.value) %>%
  arrange(desc(pct_change)) %>%
  kable
```

>>>>

dx_visit = dx %>%
  filter(!is.na(diagnosis_type)) %>%
  mutate(dummy=TRUE) %>%
  select(visit_id, diagnosis_type, dummy) %>%
  distinct() %>%
  spread(diagnosis_type, dummy)

@@

abx_visit = top_abx %>%
  select(desc, abx) %>%
  left_join(drugs, by='desc') %>%
  count(visit_id, abx) %>% ungroup() %>%
  #mutate(present=n>0) %>% select(-n) %>%
  #spread(abx, present) %>%
  #mutate_if(is.logical, function(x) if_else(is.na(x), FALSE, x))
  spread(abx, n)

visits = read_tsv_years('../../db/namcs/data/namcs_visits_%i.tsv') %>%
  mutate(age_group=case_when(.$age <= 19 ~ 'child',
                             .$age <= 64 ~ 'adult',
                             .$age <= 92 ~ 'elderly')) %>%
  left_join(dx_visit, by='visit_id') %>%
  left_join(n_abx, by='visit_id') %>% replace_na(list(n_abx=0)) %>%
  left_join(abx_visit, by='visit_id') %>%
  mutate_at(top_abx$abx, function(x) {
    case_when(is.na(x) ~ 0L,
              x == 0 ~ 0L,
              x > 0 ~ 1L)
  }) %>%
  mutate_at(unique_dx_categories, function(x) if_else(is.na(x), FALSE, x))
```

@@

```{r per_capita_models_display}
x = read_tsv('tables/model_abx.tsv') %>%
  filter(term=='year', model=='poisson') %>%
  left_join(top_abx, by=c('antibiotic'='medicare_abx')) %>%
  mutate(abx=if_else(is.na(abx), antibiotic, abx)) %>%
  mutate(data_source='medicare')

x %>% head %>% kable

y = per_capita %>%
  filter(term=='year') %>%
  mutate(data_source='namcs')

abx_levels = x %>%
  arrange(estimate) %$%
  abx

bind_rows(x, y) %>%
  add_pct_change() %>%
  mutate(abx=factor(abx, levels=abx_levels),
         abx=forcats::fct_relevel(abx, 'overall', after=Inf)) %>%
  ggplot(aes(x=abx, y=pct_change, ymin=ci_low, ymax=ci_high, color=data_source)) +
  #geom_linerange() +
  geom_errorbar() +
  geom_point() +
  coord_flip() +
  xlab('') +
  ylab('pct change in consumption per capita') +
  ggtitle('Per capita') +
  theme_minimal()

per_capita %>%
  filter(term=='year') %>%
  mutate(valid=abs(std.error/estimate)<=0.3,
         adj.p.value=p.adjust(p.value, method='BH')) %>%
  add_pct_change() %>%
  select(abx, ci_low, pct_change, ci_high, p.value, valid, adj.p.value) %>%
  arrange(desc(pct_change)) %>%
  kable
```
